Type Refinements for the Working Class

### 2015-11-12 paper.tex
notation

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the set
  of its substitutions as the following product:
  \[
    \Define{[\Omega]}{
      \prod_{\MV{m}:v} \MkSet{E\mid\IsAbtUnmoded{\cdot}{\cdot}{\cdot}{E}{v}}
    }
  \]
  Let $\Discrete{[\Omega]}$ be the discrete category on $[\Omega]$. Then, for
  any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\Discrete{[\Omega]}}}$, we can
  define the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows:
  \[
    \textstyle
    \Define{
      \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
    }{
      \Hom{\mathbb{J}}{
        \Yoneda{w}
      }{
        \varinjlim_{\Discrete{[\Omega]}}\mathcal{J}
      }
    }
  \]

  Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
  when the family of judgments $\mathcal{J}$ shall forevermore have a section
  (i.e. for any substitution $\Member{\omega}{[\Omega]}$,
  $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
  \emph{valences} rather than sorts; as such, the general judgment allows us to
  quantify over terms of higher type.  However, for clarity we will often write
  $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
  $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
  the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
  proper $\MApp{\MV{m}}{\cdot}{\cdot}$.

>>>>

\begin{definition}[General Judgment]
  For a metavariable context $\IsMetaCtx{\Omega}$, we can define the set
  of its substitutions as the following product:
  \[
    \Define{\square\Omega}{
      \prod_{\MV{m}:v} \MkSet{E\mid\IsAbtUnmoded{\cdot}{\cdot}{\cdot}{E}{v}}
    }
  \]
  Let $\Discrete{\square\Omega}$ be the discrete category on $\square\Omega$. Then, for
  any diagram $\Of{\mathcal{J}}{\mathbb{J}^{\Discrete{\square\Omega}}}$, we can
  define the general judgment $\GenJ{\Omega}{\mathcal{J}}$ as follows:
  \[
    \textstyle
    \Define{
      \left(\GenJ{\Omega}{\mathcal{J}}\right)(w)
    }{
      \Hom{\mathbb{J}}{
        \Yoneda{w}
      }{
        \varinjlim_{\Discrete{\square\Omega}}\mathcal{J}
      }
    }
  \]

  Intuitively, the general judgment $\GenJ{\Omega}{\mathcal{J}}$ is evident
  when the family of judgments $\mathcal{J}$ shall forevermore have a section
  (i.e. for any substitution $\Member{\omega}{\square\Omega}$,
  $\mathcal{J}(\omega)$ shall be evident). Recall that metavariables have
  \emph{valences} rather than sorts; as such, the general judgment allows us to
  quantify over terms of higher type.  However, for clarity we will often write
  $\GenJ{\MV{m}:\sigma}{\mathcal{J}}$ rather than
  $\GenJ{\MV{m}:\MkValence{\cdot}{\cdot}{\sigma}}{\mathcal{J}}$; likewise, in
  the body of $\mathcal{J}$ we will simply write $\MV{m}$ rather than the more
  proper $\MApp{\MV{m}}{\cdot}{\cdot}$.
